Trends from 30-year observations of downward solar irradiance in Thessaloniki, Greece

### 2023-12-18 MDPI_submission.Rmd
Commit 2023-12-18 12:14

For cloudy-sky conditions (Figure\ \ref{fig:szatrends-3}), we can not discern any significant dependence of the SDR trend with SZA as the variability of irradiance is
dominated by the cloud effects.
For SZAs $25^\circ$ - $75^\circ$, the trends range within about $\pm 0.2\,\%/y$, 
the trends are variable and for most SZAs insignificant ranging between
$0$ and $0.2%\,\%/y$.
Between $50^\circ$ and $75^\circ$ SZA the trends for the period before noon are stronger and negative, possibly associated with stronger attenuation by clouds under oblique incidence angles.

>>>>

For cloudy-sky conditions (Figure\ \ref{fig:szatrends-3}), we can not discern any significant dependence of the SDR trend with SZA as the variability of irradiance is
dominated by the cloud effects.
For SZAs $25^\circ$ - $75^\circ$, the trends range within about $\pm 0.2\,\%/y$, 
the trends are variable and for most SZAs insignificant ranging between
$0$ and $0.2%\,\%/y$.
The smooth increase of the trend at SZAs larger than
$\sim 75^{\circ}$ is probably associated with stronger attenuation by
clouds under oblique incidence angles which results in smaller
variability.

### 2023-12-18 MDPI_submission.tex
Commit 2023-12-18 12:14

For cloudy-sky conditions (Figure~\ref{fig:szatrends-3}), we can not
discern any significant dependence of the SDR trend with SZA as the
variability of irradiance is dominated by the cloud effects. For SZAs
\(25^\circ\) - \(75^\circ\), the trends range within about
\(\pm 0.2\,\%/y\), the trends are variable and for most SZAs
insignificant ranging between \(0\) and \(0.2%\,\%/y\). Between
\(50^\circ\) and \(75^\circ\) SZA the trends for the period before noon
are stronger and negative, possibly associated with stronger attenuation
by clouds under oblique incidence angles.

>>>>

For cloudy-sky conditions (Figure~\ref{fig:szatrends-3}), we can not
discern any significant dependence of the SDR trend with SZA as the
variability of irradiance is dominated by the cloud effects. For SZAs
\(25^\circ\) - \(75^\circ\), the trends range within about
\(\pm 0.2\,\%/y\), the trends are variable and for most SZAs
insignificant ranging between \(0\) and \(0.2%\,\%/y\). The smooth
increase of the trend at SZAs larger than \(\sim 75^{\circ}\) is
probably associated with stronger attenuation by clouds under oblique
incidence angles which results in smaller variability.
